\chapter{ABC Players and Storyline}

\section{Introduction}

This is an overview of the characters and storyline that this campaign has been following for a group of students that the author has been running it with. This is the first time (other than one quick session) the author has been Dungeon Master for a group of people so the story and play style varied greatly as to see what things work best.

\section{Characters}

\subsection{Gashtai}

\subsubsection{What was given to the DM}

My mother was a Kalashtar and was the victim of a band of pirates who sailed on a ship called Cerberus. Three years and nine months later the ship returned to the small town of ------. My ‘father’ found my mother, and after more abuse discovered me and took me away to raise me a pirate. For the first thirteen years came abuse, lots of deck scrubbing, and witnessing the horrors that men could inflict on others. Then I was forced to join in. I tried to refuse but I was threatened with death. When I had worked up the courage to refuse again, my father cut a gash across my right eye and threatened to return to my hometown and kill my mother and my sister, which I didn't even know I had. So, I learned to be a pirate, and to put on a show of enjoying it, but I hated every minute. I discovered I was slightly telepathic and when I could I would use it to help the victims of the crew of the Cerberus by warning them and telling them where to hide. After a raid on a small town where the crew mutilated and killed half the population I worked up my resolve and snuck off the ship in a dingy, hoping to find my mother and supposed sister before my murderous father did. 

The fates had something else in store for me and they brought on a massive storm. I barely managed to keep the dingy afloat and when the storm finally passed I found myself in unfamiliar waters with no land in sight. As the days passed I grew mad with hunger and thirst. 

That’s when Hades came to me with an offer that I was too delirious to refuse. I would become a reaper of souls for him in exchange for the power to protect the mother I barely knew and the sister I’d never met. He gifted me a tattered black cloak and a staff and fused me with the powers of life and death.

When I regained my complete cognitive senses I first realized that I had no clue where my hometown was or even if my mother was still there. I didn't even remember her name. Then I realized that I had just traded piracy for something just as perverse. My job was to kill people and collect their souls for the god of death. And this was a long contract. I was screwed.

It took me the next few weeks to find land, during which time I realized that I no longer needed food or water to sustain myself. I resolved to track down my fathers ship and crew and use my new-found power to bring them to justice and maybe wring the location of my hometown, or mother out of one of them. I knew though that there was a chance they would die before giving me the satisfaction of that information, so I also decided to search far and wide for relics or powers that would aid me in finding my long-lost family. 

On my journey, my outward appearance would be a persona of a cut throat pirate, striking fear and sometimes death into those who deserved it, while my telepathic voice would assure the innocents of their safety. 

\subsubsection{What was given to the player}

While searching for lang after becoming a reaper of souls, you had much time to think of the past. You have a distinct memory that you obtained through meditation on the past. This memory is that of your father saying ``you will never return there, you will never see -------- again!'' The only problem is you cannot recall the place said. Zelos? Zeroes? Xebulos? You cannot recall.

When the god of hades (you inferred) visited you, you were given the task of hunting down and removing Dastan from existence. You were told that the Dastan you're after is notorious for his crimes. Your most recent intelligence has led you to believe the Dastan you seek has been captured in the Tempestas prison (a major trade city). You have managed to secure passage on a spice trade ship to Tempestas. It just so happens that you've also heard of the legend of the power stones which can reverse time which you seek to help you in your search for your mother and sister, if they are still alive. Tempestas is known to have a vast assortment of knowledge which is perfect for you that Dastan is claimed to be there.

\subsection{Victor Anderson}

\subsubsection{What was given to the DM}

My character is going to be obsessed with death, but only so he can grow strong enough to pull a Hercules and save a loved one from the underworld. But during his strengthening, he became absolutely fascinated with death, and now he struggles with a purely academic obsession, sometimes forgetting his mission. He's not a creepy guy, just gets excited and eager to examine death as an energy.

He has a problem with falling for pretty girls, and one day he was greeted Zeus-style by a goddess, and she bore a daughter to him. When she was just starting to come of age, she was kidnapped by whatever version of underworld deity you choose. As payment, the god offers a pact to my character, giving him underworld power (hence, fallen aasimar). My character tricked the god by accepting, and is now studying magics that will help him siege the underworld and rescue his daughter.

\subsubsection{DM additions to backstory}

Victor Anderson. He has a problem with falling for pretty girls. One day he was greeted by a goddess who called herself Ishtar. She bore a daughter to him and told him her name was Samilah (meaning brightness of the night). Ishtar claimed this daughter would be of great importance to the entire world. When she was just starting to come of age, she was kidnapped by an un-named goddess of the underworld (Osiris). As payment, the god offers a pact to my character, giving him underworld power (hence, fallen aasimar). He tricked the god by accepting, and is now studying magics that will help him siege the underworld and rescue his daughter.

Victor is obsessed with death, but only so he can grow strong enough to pull a Hercules and save a loved one from the underworld. During his strengthening, he became absolutely fascinated with death, and now he struggles with a purely academic obsession, sometimes forgetting his mission. He's not a creepy guy, just gets excited and eager to examine death as an energy.

What isn't known is the purpose of Samilah. Samilah was created by the Celestials as a mortal containing much of the knowledge of the ascended Celestials. Her purpose was to find the San'graal and prevent it from being used to destroy the Celestials. She is then to lead the mortal followers of Celestus in the conquest of the world. 

\subsubsection{What was given to the player}

Victor, as being plagued with the lust of the flesh, you are unable to resist a pretty woman. One day, greeted by Ishtar, you were offered the opportunity to know her in exchange for raising a daughter. This daughter was to be named Samilah and was to be of great importance to the whole world. When coming of age, she was kidnapped by an un-named goddess of the underworld. The goddess would have taken her regardless but you made her think you were willing and `traded her for power.'

As a goal of finding your lost daughter, you've became obsessed with the underworld and death. You seek to conquer the underworld yourself to save your daughter. In doing so, you have been chasing legends and myths pertaining to the underworld. In your studies you have come across a reference to a `hidden place outside of this world', where `secrets of the gods powers lay', which you look at as the underworld. It is legend that there is a way to access realities outside of our own which were safely ghuarded and hidden away with Morgana.

In your search for more on these legends, you have set sail to Tempestas. Tempestas is known as a center of trade and knowledge and so you are hoping that is where your answer lies. You were able to buy passage to Tempestas via a spice trade ship and are now on your way.

\subsection{Candy Barr}

Your son (one of many) returned from a long journey, like a thief in the night. He came with his fianc\'{e}. As the mother, you naturally prepared them a great wedding. The evening went great but unfortunately no one except you awoke the next day.

After a few days of grieving, you realize that it's easier to take care of one person than many. You live peacefully for a few years but start to feel lonely. You choose to leave because you feel it's your duty to reproduce. You pack up your most valuable things, which includes a small box you had kept packed away since the wedding. It contains some recipes and a small box of spices. You get the idea to travel via a spice ship after seeing the small box and hitch a ride to Tempestas (a large trade city) in search for your long lost happiness. 

\subsection{Clime}

\subsubsection{What was given to the DM}

Nothing.

\subsubsection{What was given to the player}

You awake in prison.

\subsection{Ferrous Apollos}

\subsubsection{What was given to the DM}

Raised in a dwarf clain, I was exiled at a young age due to subpar beard growth. Wandering the wilds, a priest - a follower of Apollo took my into his church. Raised by the devout, I often seek to discuss religion and am heavily indebted to the priesthood. 

I focus on charity and healing, and my holy symbol is a small stone (about 2 inches by 3 inches), worn, round and smooth by repeated use. I had carved a basic prayer to Apollo into it when I had first been taken in, the text now difficult to make out.

Growing without my true family, I view Apollo as my true father, but as such I am not very judgmental of other faiths. However, the scar of abandonment in youth makes me find others suspect and have troubles trusting them.

\subsubsection{What was given to the Player}

You were raised in a dwarf clan in a small town named Kharanos. When young. you were very picky about your meals and did not eat fish or nuts. Because of this, your beard growth was shunted and you were exiled. 

After becoming a follower of Apollo, you were gifted a small stone (a holy symbol) that was supposedly carved from the reality stones made during creation. On the stones your younger self, while in a spiritual trance, carved a prayer onto the stones which looks like

\begin{center}
	{\Large \fontspec{D3FZ} 
	Hallowed Apollo
	
	May this gemstone provide light
	
	When darkness appears
	}\footnote{Which states ``Hallowed Apollo. May this gemstone provide light when darkness appears''}
\end{center}

You know what the prayer was you carved but due to the trance, you do not recognize the script you wrote it in.

Because of your past, you have had troubles with trust. Your church has entrusted you with a `holy calling' to spread the words of your religion to the city of Tempestas. On your long journey, you have been trying to understand your holy symbol which has led you to apparent contradictions having to do with Apollo's creation teachings and the reality stones. You've thought it necessary to try and better understand the legends and history surrounding your holy item in order to draw nearer to Apollo. It just so happens that the rich trade culture and wide spread of knowledge found in Tempestas would be the perfect place to do so.

\subsection{Darris McStickle}

Darris was not always present to the sessions so sometimes runs off or disappears from the rest of the players.

\subsubsection{What was given to the DM}



\subsubsection{What was given to the player}

You have been living in Tempestas for some time now. Unfortunately, you found a boy sitting over a cliff by a waterfall and could not control the urge to Sparta kick him off. After doing so, you were taken to prison by the city guards and have been there ever since.

\subsection{Yzom}

\subsubsection{What was given to the DM}

Yzom was found at a doorstep of an orphanage. He was the smallest kid and had to learn how to con the other kids to keep them from picking on him, wearing glasses and reading all the time didn't help his case either. over the years his ability to con got better and better and yzom started pulling cons on the rich and powerful, the bigger the highest, the more fun it was. the money was never the reason for this life of crime, it was always about the thrill, and maybe one day a big retirement.

Reading always attracted strange new ideas and conspiracy's, and somehow somewhere "the man" (government/rulers) was definitely trying to pull something over on the people. Reading and dealing with the criminal underground together brought forth learning many languages both from needing to talk to others and from needing an identity for a con that needed a new language. "Trust no one, but Give no one up." Became a motto yzom held to, it wasn't often in his line of work that he could find true friends, but regardless of how close he was to his current team, he would never give away a fellow criminal, that is at least if they haven't back stabbed him.

Never met something he couldn't either steal or con his way into getting, because of this, yzom became well known in the criminal underground giving him many connections. However, the life yzom has lived has for the most part been alone, he has never had a team he could trust for more then a few months, he is good at being alone and makes new friends fast, but has never had a close relationship. Yzom has a soft spot for kids and orphans because of his past as an orphan child. This has Driven him to stealing great wealth and donating it to orphanages.

\subsubsection{What was given to the player}

You were raised in an orphanage in the city of Tempestas. A vastly wealthy city where you learned the art of the con. In your research, you have been lead to believe that there is a conspiracy by the leaders of the major trade cities (Tempestas, Dalaran, Nar'Shadaa, Corinth, Jericho, etc...) to reform a rumored one world government that existed centuries ago. You believe there is a hidden city, Camelot where advanced technologies are being made to change the world. Your search has lead you to investigate the situation further in Tempestas where you can also donate to the orphanage you were originally from. 

You know you will need to remain low-key while in Tempestas because of some past cons you played on some higher ranking nobles. For this reason, you've secured passage to Tempestas via a trade route and spice ship and have been told to find someone named Dastan to secure passage safely out of the city. 

\subsection{Vinia Kobas}

Vinia is a member that joined late into the campaign. Vinia joined after session 07.

\subsubsection{What was given to the DM}

My story began as a child. My parents taught me the ways of the wild before they had to leave to provide food for our tribe. One day, they never returned. I had to find out what happened even though my tribe advised against it. I left them in search of truth. I searched high and low for them but they were nowhere to be found. That is until I found my parents’ bloody clothes and their weapons broken and stomped into the ground. I fell to my knees knowing that they would never return, for they were attacked by monsters. 
	
I stayed in the dirt for three days in grief. It wasn't fair. My parents always respected the wilderness, how could it attack them? I felt betrayed and bitter. I went to leave the woods forever. “Wait,” said a voice, soft and still. I turned around and saw a ghostly glowing deer. The only sound it made was from the voice. She said that she was the spirit of the forest. She explained how all of life needs to be balanced, including life and death. Though she did not cause, she didn't stop it for that reason. That was when I truly understood the druid way. She showed me how nature could be an ally. She spent all day\footnote{I discussed with the player that this would make more sense if it was a large period of time, a few weeks perhaps. She agreed.} with me teaching me spells that I would need to know. 

Before I left she also told me that I would not find my tribe where I leave them. They went missing. Where could they have gone? I felt panic setting within me. How could I find them? Where do I go? Where do I start? Before I asked her, she told me to head southwest towards the swamp. I looked in that direction and when I looked back, she was gone. What was left was a necklace made of willow tree branches and leaves. It must have been left for me. After all the willow tree represents balance and growth, which is what this life has intended for me. With it on, I set out to find my tribe. Little did I know what awaited me in the swamp.

\subsubsection{What was given to the player}

You are a young druid. You have been told all of your life that the tribe you are in is among one of the few safe places in the surrounding forest (for a young elf like you). You were told by your parents to never wander too far from home. Despite their warning, you've ran off a few times when they were sleeping to see the region for its beauty, so you are slightly familiar with various parts of the forest.

Your mother always wore a golden necklace infused with the tooth of a displacer beast (one of the majestic predators of this region). You did not find the necklace when you found your dead parents. Since you left the spirit of the forest, you've seen a few wild creatures (which is not unusual). The unusual thing that stuck you though is that you don't recognize any of them even though you've grown up here your whole life. Similarly, the sounds of the forest and wind seem... off to you. 

When heading south towards the `swamp', you came across a huge cliff/drop. All you could see is fog at the bottom and the cliff you and the forest are on, which was far too steep to climb down. You used your skills and courage to mount a large winged creature (this took a few days and some patience) and use it to glide down. You knew this was what you needed to do but as soon as you entered the fog and could no longer see, you wished you hadn't taken the leap.

\subsection{November (NR-48)}

NR-48 is a character that joined late into the campaign. DR-48 joins the story after session 12. This is a character played by Ferrous Apollo after his character brutally committed suicide because he did not like his character.

\subsubsection{What was given to the DM}

NR-48 was a soldier. Not by choice, by function. He deleted memories, but hangs on to his rank insignia out of habit. After the war, he lived a simple life, distancing himself from others out of fear, despite his own love of making friends. He fears he'll hurt those he loves if he gets too close. He seeks a wise counselor to help him get over his fears; his life goal is to find a worthy cause and lend his hand to their success.

\subsubsection{What was given to the player}

After the war, you retreated to a dense forest to separate yourself from others. After years of living in this forest, you learned to avoid the dangers of the area by avoiding many of the large threats that lurk throughout. One day on a long hunt, you came across a sheer drop overlooking a vast forest. While there, you were attacked by a small displacer beast (one of the dangerous predators of the area). You managed to scare the beast off, but first suffered some deep wounds and in the process lost some of your equipment to the cliff. Of the things lost, your rank insignia was among them. You could see a potential way down, but you could not see a perceivable way back up. You took the leap. You fashioned a parachute and headed down.

You retrieved your items but were now in a completely different region of forest that was unfamiliar to you. After a few weeks of traveling, hunting, surviving and exploring, you came across a large tower, which was home to a wizard named Baba. Baba seemed to have a deep understanding of your fears and need for a counselor and was able to relate to you well. She convinced you to stay with her for a few days in the hopes that you would be needed for a worthy cause. She could not spend a lot of time discussing and counseling because she appeared to have something very important happening with her studies, but she did provide you with a place to stay, information about the area and food. 

\section{The Adventures}

\input{Chapters/Sessions/Session01}
\input{Chapters/Sessions/Session02}
\input{Chapters/Sessions/Session03}
\input{Chapters/Sessions/Session04}
\input{Chapters/Sessions/Session05}
\input{Chapters/Sessions/Session06}
\input{Chapters/Sessions/Session07}
\input{Chapters/Sessions/Session08}
\input{Chapters/Sessions/Session09}
\input{Chapters/Sessions/Session10}
\input{Chapters/Sessions/Session11}
\input{Chapters/Sessions/Session12}