\section{Camelot and the San'graal}

\begin{center}
	{\Large\fontspec{Anquietas} 
		Only those of virtue true can win the prize concealed. Beyond the reach of the flawed and tainted, the San'graal shall instead belong to he who speaks the guardians name. Prudence, wisdom, charity, kindness, and faith; let these be your guide on this perilous quest.
	}
\end{center}

which translates to

\begin{center}
	Only those of virtue true can win the prize concealed. Beyond the reach of the flawed and tainted, the San'graal shall instead belong to he who speaks the guardians name. Prudence, wisdom, charity, kindness, and faith; let these be your guide on this perilous quest.
\end{center}

In the library where this message was given is an older gentleman who also claims to have a map. At the time of their arrival in the village, the Celestial followers also arrive and burn all of the books in the area. The elder gentleman (Samilah in disguise) is also after the San'graal. He will lead them towards what the map showed which uncovers various puzzles. 

The first puzzle requires prudence (patience and carefulness). This is an invisible maze of temporal fluctuations. The maze can be navigated in various ways but must be done so carefully.The second is a barrier that closes the party in with a chest in the middle. Within the barrier, they will find one of the villains from earlier in the campaign. This man is also after the San'graal. The key to this puzzle is charity. If each player places something inside the chest, the barrier will fall.

The gentleman will at some point use some sayings from the Book of Celestas such as "the truth eludes he who does not seek it" (A quote from the book of Celestas). And if the party notices that this is from the book, they may be able to perceive through Samilah's disguise. 

The path leads to the cave under a mountain and within the cave is where the map led. The third riddle is "choose the way that is just and true" written on the wall. To the left is a weeping child, to the right is an empty hallway. The child runs away and finds himself trapped behind some bars. After everyone tries to lift the bars, they open. and the child disappears. A path appears behind the cave. The fourth "I'm struck and cut, shaped and cooled, then bound by the rings to release what is stored." The answer is key. "The more you take, the more you leave behind." The answer is footsteps. If the party turns around, the passage will be sealed behind them. The fifth is a flaming wall the party must have faith and walk through it. At the end, a bridge overlooking nothing with a gem on the other side. The gem is a hologram. When touched, a dragon will appear. After speaking the Guardians name (Myrddin) the stone is still a hologram, but after reaching for it, the party is transported to Myrddin’s lab where they find Myrddin in stasis. After coming out of stasis, Myrddin recognizes the party (but with all different names) and refers to them as their knights, However, he refers to the criminal as a traitor and silences him.
