\section{Emporium of Grotto}

Due to the influence of the space-time stones, a facility from the far future and from a distance location can be accessed from a cave within the Pluvian Forest. The cave has within it a modern bulkhead door leading to a laboratory from a future protagonist named Goto. Gotto specializes in creating artificial intelligence and robotics. This is from a far futuristic time.  The laboratory is sealed by a panel which simply has the numbers 0-8 on it (a keypad with three rows of three). The keypad will be of an unknown language and appear as the following.

\begin{center}
	{\Huge \fontspec{Hymmnos}
		OOOO
		
		0 1 2
		
		3 4 5
		
		6 7 8
	}
\end{center}

The four circles on the top represent LED lights. These will turn on and off with various colors depending on what is entered. When a number is entered the first will light red. After this, the second will light red when another is entered. Once all 4 numbers are entered, if the code sequence is wrong the lights will flash red twice and emit an error noise. If the code is entered correctly, the lights will turn blue and the door will open. Above the cave is written the following.

\begin{center}
		{\Huge \fontspec{Hymmnos}
			Emporium of Grotto
			
			Go away
		}
\end{center}

This reads ``Emporium of Grotto Go away''. Throughout the cave are intelligent robotic orbs floating around that will speak to the party and attack them if they are found to be seeking the lab or dangerous to Gotto’s personal belongings. Regardless, these robots have a bug which causes them to sputter sensitive information when they are destroyed. In this case, the robots will spout numbers of the door code only in binary. The first robot killed will yell ZERO ZERO ZERO. The second will yell ZERO ONE ZERO. The third will yell ONE ONE ZERO, and the final will yell ONE ZERO ONE. Giving the binary numbers of 000, 010, 110, 101, which translates to 0, 2, 6, 5 which is the correct number sequence to open the door. 

Once inside the laboratory, there will lay a robotic sphere that is deactivated in one corner of the room. The party can reactivate said sphere by touching it. This sphere will follow the party around and possibly give suggestions and help towards future quests. Along with this, there is also some precious materials found in this lab if they start searching through drawers. There is also a scanner that will serve no purpose at first, but can come in handy later in the campaign if something temporal or invisible is needed to be found.
