\section{Puzzles}

\subsection{Corridor of reverse sight}

The party approaches a dead end in a corridor. When they turn around, the corridor they came to is sealed off with a wall. In both directions they cannot walk. On the dead end they approached, it states in an old dialect ``Place your eyes upon this text, and make it appear small.'' They key is to look directly at the text and walk backwards which will make the text seem small. By doing so, the party will enter a new room.


\subsection{Paintings of Holding}

The party is trapped in a room full of small objects and realistic paintings. The paintings include the following

\begin{itemize}
	\item \textbf{A Summer Picknick}. This depicts two people supposedly in love having a picknick with food and a blanket in a nice summer valley. The only problem is there is no picknick basket.
	\item \textbf{A Battle of Heroes}. This depicts a dark overseer fighting what looks like a hero. Both have incredible looking weapons and there are corpses and weapons laying on the ground, one of which looks exemplary.
	\item \textbf{The Life of a Petunia}. This features a simple table.
	\item \textbf{Fountain of Alexandria}. This features a fountain with no water.
	\item \textbf{The Never Ending Needs}. This painting features a young boy holding a bag out begging for food and money from what look like really well off folk wandering the streets of a town. The bag is a bag of holding, which must be in the painting to move on, however it can contain items that the party can acquire from it.
	\item \textbf{The King's Vault}. This is a painting of a king with his back turned to the image. He has a large purple cape and a large golden crown on his head. In front of him are large piles of treasures, with chalices and gemstones, and more.
\end{itemize}

Some items around the room include

\begin{multicols}{3}
	\begin{itemize}
		\item A picknick basket
		\item A flower pot
		\item A mug
		\item A carpet
		\item A table
		\item A broken pocket watch
		\item A small silk rope
		\item Three large golden coins
	\end{itemize}
\end{multicols}

The key to this is that there are objects laying around the room that match the missing items in the paintings. The players can place items into or remove items from the paintings. They must place items in the paintings so that the names of the paintings match what they are called. They may also remove items in the paintings if they are not needed for that painting. Upon doing so, the entrance to the room will open.

\subsection{Chronological Tapestry}

The party enters a room full of lavishly painted tapestry on one wall. The tapestry is painted with events that the party has lived through. The key to this room is to place the tapestries in chronological order to leave.

\subsection{Statue of the Disarmed}

The party enters a room with a statue of a knight, with a slot in its clenched fist where a weapon should go. Once a worthy weapon has been placed in its hand (a sword but not a dagger, or a magic sword instead of a normal sword), the statue comes to life. When the party has defeated it, the statue shatters, leaving the weapon and a key (or other treasure) in the debris.

Taken from https://dwarvenforge.com/forum/viewtopic.php?t=2308

\subsection{Room of Off-Balance}

The floor is lined with shapes and furniture in which half is placed within the lines and half is slightly offset. On the ceiling is a chandelier that hits the ceiling offset from the center. On the chandelier is the writings ``Room of Off-Balance''. The key to this room is to make everything off-balanced from it's designated spaces.

\subsection{Eight Queens of Peace}

In this puzzle, the players are given a chessboard and eight queens. They must place the queens such that they cannot attack one another. There are 12 different solutions to this.

Solutions can be found at https://en.wikipedia.org/wiki/Eight\_queens\_puzzle

\subsection{Alphabetical Number}

What is special about this number? 8549176320. Answer: The digits are in alphabetical order (in English).

\subsection{Statement of Provability (HARD)}
	
Someone named Raymond Smullyan\footnote{Adapted from Logical Labyrinths, 2008. Smullyan related this puzzle to G\"{o}del’s incompleteness theorem. “I thought of the penny as standing for provability and the quarter as standing for truth. Thus the statement ‘You will not give me the penny’ corresponds to G\"{o}del’s sentence, which in effect says: ‘I am not provable.'”} approaches the party and says``Here are two objects, a key and a stick. Make a statement. If your statement is true, then I’ll give you one of these objects (not saying which). But if your statement is false, then I won’t give you either. There is a statement you can make such that I would have no choice but to give you the key (assuming I keep my word).''

One statement that works is “You will not give me the stick.” If that were false, then I would give you the stick. But I’d said that if your statement were false I’d keep both objects. So your statement can’t be false; it must be true. And if you’ve made a true statement then I owe you an object. So I have no choice but to give you the key.

\subsection{The Water Jug Problem}

Two jugs labeled ``IIIII'' and ``III'' (with tick marks) are sitting next to a fountain that appears to never run dry. Next to them is a large stone, with a circle indent (matching the size of the jug) that says ``IIII'' on it. Given a 5-gallon jug, a 3-gallon jug, and a limitless supply of water, how can you measure out exactly 4 gallons?

\begin{enumerate}
	\item Fill the 5-gallon jug and use it to fill the 3-gallon jug. That leaves 2 gallons in the 5-gallon jug.
	\item Empty the 3-gallon jug and transfer the 2 gallons from the 5-gallon jug to the 3-gallon jug.
	\item Fill the 5-gallon jug and use it to top off the 3-gallon jug. That requires exactly 1 gallon, leaving 4 gallons in the 5-gallon jug.
\end{enumerate}

OR

\begin{enumerate}
	\item Fill the 3-gallon jug and empty it into the 5-gallon jug.
	\item Fill the 3-gallon jug again and use it to top off the 5-gallon jug. This leaves 1 gallon in the 3-gallon jug.
	\item Empty the 5-gallon jug. Transfer the remaining gallon from the 3-gallon jug to the 5-gallon jug.
	\item Fill the 3-gallon jug again and pour it into the 5-gallon jug
\end{enumerate}

\subsection{Freedon Nadd's Tomb, Vault}

Upon entering, the players will see

\begin{center}
	The truth will set you free
	
	(6 \_ 2) \_ 8 \_ 9 \_ 1 = 13 
	
	+ - * / 
\end{center}

This is in a wall made of sand. They have to fill in the operations\footnote{Puzzle from Star Wars: Knights of the Old Republic II.}. They can only use each operation once, and must make the statement true. The answer is (6 * 2) - 8 + 9 / 1 = 13. As they use the operators by drawing them in, they disappear from the bottom row.


\subsection{Traversing the Clouds}

Transported to another dimension, the players find themselves walking on the sky. Clouds are below them and the air is thin. Above them is the planet, upside down. They are each given a bag of weighty holding\footnote{A Bag of holding that maintains it's weight of what is inside.}. The key is to find a storm cloud that is about to rain, or just water vapor from the clouds around them. This water will fall to earth (travel upward relative to them) and with enough of it they will be pulled up to earth. When falling upward, they will escape the region. 

\subsection{To Remove a Reflection}

The party is placed in a dark room, they have nothing but magical glow sticks. No other fires can be lit in here due to the very humid air. The torches are magical torches to last endlessly. Within the room, the floor is filled with a shallow layer (1-2 inches) of a very reflective liquid. The party members can see their reflections wherever there is a light. They appear to be in what is a never ending dark cavern extending forever. Throughout the cavern, the party sees unlit torches laying on the ground with skeletal remains. On one corpse, there is what appears to be a small stand made of skeletal remains. On the stand lays a journal of a past visitor. Within the journal are stories pertaining to days in the cavern. Among the writings, one thing that stands out is the last thing written in the journal which is ``The only company I have in this place is that of my reflection. Unfortunately it follows me everywhere and I cannot lose it.''

The key to this puzzle is the party has to put all of their glow sticks out by destroying him. When their reflections are hidden, a path to the exit is illuminated.


