\section{Auru Convallis}

This is the area to the East of Aurushire. This area is unexplored and all is known about it is that it is heavily dense with mountainous and forest terrain and the only known entrance path into the mountains is through the southern shore which is blocked by a hostile Naga tribes and other creatures. The shore just to the East of the Nagas is a foggy swamp and marshland. The region is hard to see and contains many creatures that the party could encounter. To the East of the swamp is a small beach and then further is large rock-faces with sharp jagged rocks (unclimbable). This beach is to serve as a good ship wreck location for the party on their way to Aurushire/Statu. With this option, they only have the option to traverse through the swamp or hard to traverse mountainous forest just north of the swamp.

\begin{commentbox}{Convallis Swamp Encounters}
	Here are various encounters the party can face in the Convallis Swamp. The page numbers listed are which page these encounters are in the Monsters Manual. 
	
	\hline
	\begin{description}
		\begin{multicols}{2}
			\item[1:] Banshee (Page 24)
			\item[2:] Vine blight (Page 33)
			\item[3:] Cloaker (Page 42)
			\item[4:] Shadow Demon (Page 65)
			\item[5:] Vrook (Page 65)
			\item[6:] Yochlol (Page 66)
			\item[7:] Lemure (Page 77)
			\item[8:] Dryad (Page 122)
			\item[9:] Water elemental (Page 126)
			\item[10:]  Ghost (Page 147)
			\item[11:] Gibbering Mouther (Page 158)
			\item[12:] Grell (Page 173)
			\item[13:] Grick alpha (Page 174)
			\item[14:] Invisible Stalker (Page 193)
			\item[15:] Myconids (Page 233)
			\item[16:] Naga (Page 234)
			\item[17:] Piercer (Page 253)
			\item[18:] Roper (Page 262)
			\item[19:] Water Werid (Page 300)
			\item[20:] Wraith (Page 303)
		\end{multicols}
	\end{description}
\end{commentbox}