\section{The Statu Peninsula}

The Statu peninsula (commonly referred to as just Statu) is largely un-mapped area. As the name suggests, Statu is a peninsula that cannot be accessed from foot to the north. It contains very dense forestation and mountainous regions to the northern area that are not possible to travel through. The south is colonized by Aurushire where a small number of people settle. There are generally a small number of visitors to Statu, save those who are trading and working with the mines to the East of Aurushire. The best way to access Statu is through the Aurushire port.

To the West of Aurushire, there is a large forest that is significantly less dense than the northern regions. To the north of this is very dense un-explored forest and mountainous regions. Directly north of Aurushire is The Pluvian Forest. This region is not very often visited. Strange occurrences pertaining to what some call 'strange spatial events' occur in The Pluvian Forest which generally ward off visitors. To the east of Aurushire, there is a hostile tribe of river Naga which attack travelers and visitors on sight. Because of this, the area to the east and the forest regions to the east of Aurushire are largely unexplored. What is known of this region is that there is a large valley that leads from the Naga camps into the mountain/forest region. These are just north of the shore.

Also to the East of Aurushire is a large shoreline that extends a few days journey. The shore is boundaries by the ocean and sharp mountainous rock faces that are virtually unclimbable. The shore directly to the east of Aurushire is a very shallow and rocky region for a few miles. This region has regions where the mud has undergone chemical reactions over time to become firm and hard much like concrete. This makes the region semi-easy to travel through with the only challenge being the shallow water covering the entire region. Directly to the east of this area is marsh and swamplands that extend for another 40-50 or so miles. This takes about 2-3 days to journey through. Continuing further, as the marsh levels off, there is a dense region of Jungle that is nearly untouched by people due to the danger it poses to travelers. Even further east is sheer rock face and not traversable. The marsh area is covered by a thick fog that makes it hard to see anything and is home to a vast amount of creatures. All three coastal regions are surrounded by huge rock faces.