\section{The Eternal Marsh}

This marsh is an area east of Aurushire along hte coast of southern Statu on the Statu Peninsula. The area is approximately 40-50 miles long. The marsh is completely covered in a thick and dense fog. There is a small amount of volcanic activity under the marsh that creates a warm mist throughout the area. The entire area has a thick mud covering and is always damp. There is a large assortment of plant life which mainly consists of fungi, roots, mosses, and small shrubs. There is also a large amount of wildlife living within the marsh. There is a large settlement of Myconids living in this region, as well as many enchanted creatures and lurking dangers.

\begin{commentbox}{Eternal Marsh encounters}
	The eternal marsh contains a large assortment of creatures and various encounters the party can find. The difficulty of course will depend on the party size and level. However, here is a base list of some things the party can encounter within this area based on a d20 roll.
	
	\begin{itemize}
		\item 1 : Banshee (Page 24) \\
		\item 2 : Vine Blight (Page 33) \\
		\item 3 : Cloaker (Page 42) \\
		\item 4 : Shadow Demon (Page 65)\\
		\item 5 : Vrook (Page 65)\\
		\item 6 : Yochlol (Page 66)\\
		\item 7 : Lemure (Page 77)\\
		\item 8 : Dryad (Page 122)\\
		\item 9 : Water Elemental (Page 126) - These elementals can appear out of the water and form various shape changes within the marsh. They can also make themselves clothed in mud giving them extra damage and abilities. \\
		\item 10: Gibbering Mouther (Page 158) \\
		\item 11: Grell (Page 173)\\
		\item 12: Grick Alpha (Page 174)\\
		\item 13: Invisible Stalker (Page 193)\\
		\item 14: Myconids (Page 233) - The Myconids live all throughout this area. They have different villages and various underground caverns that they live in. The Myconids are non-hostile unless provoked.\\
		\item 15: Nagas (Page 234)\\
		\item 16: Piercer (Page 253)\\
		\item 17: Roper (Page 262)\\
		\item 18: Water Weird (Page 300) - The water weirds can appear in groups or by themselves. They can move from puddle to puddle within the marsh and attack in solo or work together and attack enemies.\\
		\item 19: Wraith (Page 303)\\
		\item 20: Ghost (Page 147) - Many ghosts roam the eternal marsh and have been for what seems like eternity. The ghosts can cause whispers to appear through the fog which can cause madness among players.
	\end{itemize}
\end{commentbox}


