\section{Aurushire}

Aurushire (also commonly referred to as Goldshire) is a small village located on the southern end of the Statu peninsula. Just East of Aurushire is a large mountain containing mine shafts used for gold mining. It is not well known, other by those who work in the mines, but strange things happen within these mines where mined gold will spontaneously be regrown after being removed from the mines. This phenomenon is where Aurushire (Goldshire) retreived its name from and is thought to be related to the spacial occurrences reported in The Pluvian Forest. 

\subsection{NPC's}

Aurushire is full of NPC characters. Many of them are just normal workers or village folk, however some serve an important purpose.

\begin{monsterbox}{Arryn}
	\begin{hangingpar}
		\textit{Halfling Wizard, Neutral Good}
	\end{hangingpar}
	\dndline%
	\basics[%
	armorclass = 17,
	hitpoints  = 172,
	speed      = 40 ft
	]
	\dndline%
	\stats[
	STR = \stat{12}, % This stat command will autocomplete the modifier for you
	DEX = \stat{12},
	CON = \stat{16},
	INT = \stat{20},
	WIS = \stat{18},
	CHA = \stat{18}
	]
	\dndline%
	\details[%
	% If you want to use commas in these sections, enclose the
	% description in braces.
	% I'm so sorry.
	languages = {Common, Elvish, Dwarvish, Gnomish, Halfling, Orc, Pandaren},
	challenge = 10
	]
	\dndline%
	\begin{monsteraction}[Mystical Senses]
		If a target tries to deceive you, it must make a DC19 deception saving throw.
	\end{monsteraction}	
	\begin{monsteraction}[Water sight]
		You can see clearly up to two miles over water.
	\end{monsteraction}
	\monstersection{Actions}
	\begin{monsteraction}[Bladesinger: Extra Attack]
		You can attack twice on your turn.
	\end{monsteraction}
	\begin{monsteraction}[Hold Monster]
		A creature you can see within 90 feet must succeed on a wisdom saving throw or be paralyzed for 1 minute. Target can make a wisdom saving throw at the end of each of it's turns to end the spell.
	\end{monsteraction}
	\begin{monsteraction}[Magic Jar Master]
		Allows Arryn to use Magic Jar on a nearby jar instantly and without being in a jar himself.
	\end{monsteraction}
	\begin{monsteraction}[Magic Jar]
		Long description, look it up.
	\end{monsteraction}
	\monstersection{Description/Information}
	Arryn is the first NPC most encounter when entering Aurushire from sea. He is the watcher of the ports and lives on a small farm right at docks where all sea traffic enters from.
\end{monsterbox}